Deuteron Electro-Disintegration at Very High Missing Momenta

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

by the new Super High Momentum Spectrometer (SHMS) and the High Momentum Spectrometer (HMS), respectively. The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as 

@@

where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K=E_{\mathrm{f}}p_{\mathrm{f}}$ is a kinem-

@@

@@

\noindent atical factor, $f_{\mathrm{rec}}=\frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$ is the recoil factor and $\sigma_{\mathrm{cc1}}$ is the

@@

@@

under grant No. D2-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship

>>>>

by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively. The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as 

@@

@@

\newpage

@@

\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor\footnote{The kinematical factor in Eq.\ref{eq:1} is defined as $K\equiv E_{\mathrm{f}}p_{\mathrm{f}}$, where $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.},
$f_{\mathrm{rec}}$ is a recoil factor\footnote{The recoil factor in Eq.\ref{eq:1} is obtained by integrating over the deuteron binding energy in the 6-fold differential cross section and is defined as $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$, where
          $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.} and $\sigma_{\mathrm{cc1}}$ is the

@@

\indent In conclusion, additional measurements of the $^{2}\mathrm{H}(e,e'p)n$ would be required to reduce the statistical uncertainties in this very high missing
momentum region ($p_{r}>500$ MeV/c) to better understand the large deviations observed between the different models and data.

@@

under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}. At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are
suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.

>>>>

to $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$ and neutron recoil momenta up to $p_{r}\sim 1$ GeV/c which is almost double of the maximum recoil momentum measured in Hall A \cite{PhysRevLett.107.262501}.
Measurements at such large $Q^{2}$ and high missing momenta required scattered electrons to be detected at about 8.5 GeV/c which was only made possible with the newly commissioned Hall C Super High Momentum Spectrometer (SHMS).
At the selected kinematic settings with neutron recoil angles between $35^{\circ}$ and $45^{\circ}$, MEC and IC are suppressed and FSI are under control giving access to high momentum components of the deuteron wave function.

### 2020-03-17 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 04 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by March 02, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

%\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
\input authorlist.tex

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version 04 as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu, \tt boeglinw@fiu.edu, \tt jones@jlab.org} by April 10, 2020}
\centerline{INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

%\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q$^{2}$}
%\title{$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$}
\title{Deuteron Electro-Disintegration at Very High Missing Momenta}
\input authorlist.tex
